Binary companions of red giant stars with APOGEE DR14

### 2018-02-24 paper/1-catalog/twoface-catalog.tex
Restructure and outline

\section{Results}
\label{sec:results}

\subsection{Inferring the excess variance distribution}
\label{sec:inferjitter}

@@

\subsection{Catalog of posterior samplings for APOGEE DR14 RGB stars}
\label{sec:fullcatalog}

@@

\subsection{A catalog of confident companions} \label{sec:conf-companions}

@@

\todo{Some highlights from this catalog.}

@@

Return to our various assumptions and make sure that we discuss them
\emph{by name} here.

@@

@@

\software{
% The code used in this project is available from
% \url{https://github.com/adrn/TwoFace} under the MIT open-source
% software license.
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    % \package{corner} (\citealt{Foreman-Mackey:2016}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}).
}

>>>>

\section{Experiment: infer the excess variance distribution}
\label{sec:inferjitter}

@@

\section{Results: companion catalogs}
\label{sec:results}

@@

\todo{Stuff about full catalog of posterior samples, available online}

\subsection{Stars with confident companions}
\label{sec:catalog-confident}

@@

\todo{Examples of stars with no companions at various num. epochs}

\todo{Examples of stars that meet K cut at various num. epochs}

\subsection{Confident companions with highly constrained orbits}
\label{sec:catalog-multimodal}

\todo{Many examples of stars that meet K cut but solutions limited to a few
qualitatively different solutions}

\subsection{Confident companions with effectively uniquely determined orbits}
\label{sec:catalog-unimodal}

\todo{Many examples of stars that are probably unimodal}

@@

\todo{Return to our various assumptions and make sure that we discuss them
\emph{by name} here.}

@@

\subsection{Population inference}

Comment on things we could do with these samples hierarchical inference...

We are SB1 only, but should do SB2 as well - no reason to restrict.

\section{Conclusions}

Tables available online, full code open source.\footnote{The code used in this
project is available from \url{https://github.com/adrn/TwoFace} under the MIT
open-source software license.}

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}).
}
